### 2016-10-12 EC17-submitted/mutable-filters.tex
Copying remaining files to EC17-submitted

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Security Results for Mutable Hash-Based Filters}
\begin{itemize}
\item Prove privacy of ``Stable'' Bloom Filters
\item Ditto for count-min sketch (with and without conservative update)
\item Ditto for scaling BF 
\item Correctness and soundness bounds for these?  (Not sure this is possible without a lot of work; see what's already been done in the papers that propose them)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
